From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-08 Pi+/paper/finite.tex
Fixes in sec finite

% High-level explanation of technical devices
First, we will define the required notions of free groups and group presentations, and state some of their most
important properties. Then, we introduce our chosen \emph{Coxeter presentation} for $\Sn$. To solve the word problem for
$\Sn$, we will use a rewriting system, with a suitable, well behaved collection of reduction rules corresponding to the
Coxeter presentation. Finally, we describe the normal forms in this rewriting system, using Lehmer codes, and prove the
correspondence between them and the type $\Aut[\Fin[n]]$ of automorphisms on a finite set. The generators and relations
we use here will be used to quote back to 1 and 2-combinators in $\PiLang$ (see~\Cref{sec:equivalence}).

@@

\begin{toappendix}
  \subsection{Groups}

  From universal algebra, a group is simply a set with a 0-ary constant $e$ (the neutral element), a binary operation
  $\blank\mult\blank$ for group multiplication, and a unary inverse operation $\inv{\blank}$. The neutral element has to
  satisfy unit and inverse laws, and the multiplication has to be associative (see~\Cref{def:group}).

@@

\begin{toappendix}
  \begin{definition}
    \label{def:free-group}
    Given a set $A$, the free group $F(A)$ on it is given by a higher inductive type with the following point and path
    constructors. Notice the similarity with the definition of a group structure (\Cref{def:group}), but note that each
    operation here is a generator for $F(A)$.
    \begin{itemize}
      \item An inclusion function $\eta_{A} : A \to F(A)$
      \item A multiplication function $m : F(A) \times F(A) \to F(A)$
      \item An element $e : F(A)$
      \item An inverse function $i : F(A) \to F(A)$
    \end{itemize}
    \smallskip
    \begin{itemize}
      \item For every $x, y, z : F(A)$, a path $\term{assoc} : m(x, m(y, z)) \id m(m(x, y), z)$
      \item For every $x : F(A)$, paths $\term{unitr} : m(x, e) \id x$ and $\term{unitl} : m(e, x) \id x$
      \item For every $x : F(A)$, paths $\term{invr} : m(x, i(x)) \id e$ and $\term{invl} : m(i(x), x) \id e$
      \item A 0-truncation, for every $x, y : F(A)$ and $p, q : x \id y$, a 2-path $\term{trunc} : p \id q$
    \end{itemize}
  \end{definition}
\end{toappendix}

@@

\begin{proposition}[Universal Property of $F(A)$]
  \label{prop:free-groups}
  Given a group $G$ and a map $f : A \to G$, there is a unique group
  homomorphism $\extend{f} : F(A) \to^G G$ such that $\extend{f} \comp \eta_A
    \htpy f$. Equivalently, composition with $\eta_A$ gives an equivalence $F(A)
    \to^G G \eqv A \to G$. Alternatively, the type of group homomorphisms $h :
    F(A) \to^G G$ satisfying $h \comp \eta_A \htpy f$ is contractible.
  \begin{toappendix}
    % https://q.uiver.app/?q=WzAsMyxbMCwyLCJBIl0sWzAsMCwiRihBKSJdLFsyLDAsIkciXSxbMCwxLCJcXGV0YV9BIl0sWzAsMiwiZiIsMl0sWzEsMiwiXFxleHRlbmR7Zn0iLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbMyw0LCJcXGlkIiwwLHsic2hvcnRlbiI6eyJzb3VyY2UiOjIwLCJ0YXJnZXQiOjIwfSwic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoibm9uZSJ9LCJoZWFkIjp7Im5hbWUiOiJub25lIn19fV1d
    \[\begin{tikzcd}
        {F(A)} && G \\
        \\
        A
        \arrow[""{name=0, anchor=center, inner sep=0}, "{\eta_A}", from=3-1, to=1-1]
        \arrow[""{name=1, anchor=center, inner sep=0}, "f"', from=3-1, to=1-3]
        \arrow["{\extend{f}}", dashed, from=1-1, to=1-3]
        \arrow["\id", Rightarrow, draw=none, from=0, to=1]
      \end{tikzcd}\]
  \end{toappendix}
\end{proposition}

Following the universal-algebraic definition, in HoTT, we could use a naive higher inductive type to define the free
group, which enforces the group axioms by adding path constructors (see~\Cref{def:free-group}).
Using the induction principle, we can easily verify the universal property. However, since this definition of $F(A)$ has
lots of path constructors corresponding to each group axiom, characterising its path space is difficult.

@@

Before, the only way to decide the equality of two elements in a group was to evaluate and check them on the nose, but
in a group presentation, this is reduced to a \emph{word problem}, that is, deciding whether one word -- a
representative of the equivalence class of the group's elements, can be reduced to another word, using the group's
relations. However, these equations are not directed, so it is not always possible to construct a well-behaved rewriting
system. In general, the word problem for groups is known to be undecidable.\jk{Example?}\todo{Examples: empty relation,
  full relation, van Kampen of $\pi_{1}$}

% This can be thought of as word reductions in a rewriting system.

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, s_1}};
      \node[font=\large] at (1, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1.6, 0)
      {braid={ 1, 1}};
    \end{tikzpicture}
    \caption{$\cancel$}
    \label{fig:coxeter-a}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, 1}};
      \node[] at (0.7, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1, 0)
      {braid={ 1, s_1 }};
      \node[font=\large] at (1.9, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (2.4, 0)
      {braid={ 1, s_1}};
      \node[] at (3.1, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (3.4, 0)
      {braid={ s_1, 1}};
    \end{tikzpicture}
    \caption{$\swap$}
    \label{fig:coxeter-b}
  \end{subfigure}
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (0, 0)
      {braid={ s_2, s_1, s_2}};
      \node[font=\large] at (1.4, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (2, 0)
      {braid={ s_1, s_2, s_1}};
    \end{tikzpicture}
    \caption{$\braid$}
    \label{fig:coxeter-c}
  \end{subfigure}
  \caption{Braiding diarams for Coxeter relations.}
  \label{fig:coxeter-braid}
\end{figure}
\todo{an example/motivation from book.pdf}

This construction is called a Coxeter presentation of $\Sn$. Writing it formally, we encode the rules discussed above
using a relation $\cox$ on $\List[\Fin[n]]$ (\Cref{def:cox}), and then take its congruence closure $\cox*$
(\Cref{def:coxstar}).

@@

For this to work, we first need the system to have the termination property, meaning that there are no infinite
reductions. We observe that after throwing out reflexivity and symmetry, the right hand sides of the relations $\cox*$
are strictly smaller than the left hand sides, in terms of the lexicographical ordering on words in $\Fin[n]$ (which is
well-founded). Thus, by directing the relation from left to right, we would get the termination property out of the box.
Second, we need the normal forms to be unique, so that we can get a normalisation function. This will be true if the
rewriting system is confluent -- meaning that all critical pairs, that is, terms with overlapping possible reduction
rules, have to converge. For example, in our system, the pairs in~\Cref{fig:critical-pairs-converging} converge.
Unfortunately, this is not true for all critical pairs -- an  example is in~\Cref{fig:critical-pairs-non-converging},
where left and right endpoints are normal with respect to the $\cox*$ relation.

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.35\textwidth}
    % https://q.uiver.app/?q=WzAsNixbMSwwLCJcXHRhdV8yXFx0YXVfMVxcdGF1XzJcXHRhdV8xXFx0YXVfMiJdLFswLDEsIlxcdGF1XzFcXHRhdV8yXFx0YXVfMVxcdGF1XzFcXHRhdV8yIl0sWzIsMSwiXFx0YXVfMlxcdGF1XzFcXHRhdV8xXFx0YXVfMlxcdGF1XzEiXSxbMCwyLCJcXHRhdV8xXFx0YXVfMlxcdGF1XzIiXSxbMSwzLCJcXHRhdV8xIl0sWzIsMiwiXFx0YXVfMlxcdGF1XzJcXHRhdV8xIl0sWzAsMSwiYnJhaWQiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFswLDIsImJyYWlkIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbMSwzLCJjYW5jZWwiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFszLDQsImNhbmNlbCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzIsNSwiY2FuY2VsIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbNSw0LCJjYW5jZWwiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dXQ==
    \adjustbox{scale=\scalef,center}{
      \begin{tikzcd}
        & {\tau_2\tau_1\tau_2\tau_1\tau_2} \\
        {\tau_1\tau_2\tau_1\tau_1\tau_2} && {\tau_2\tau_1\tau_1\tau_2\tau_1} \\
        {\tau_1\tau_2\tau_2} && {\tau_2\tau_2\tau_1} \\
        & {\tau_1}
        \arrow["\braid"', squiggly, from=1-2, to=2-1]
        \arrow["\braid", squiggly, from=1-2, to=2-3]
        \arrow["\cancel"', squiggly, from=2-1, to=3-1]
        \arrow["\cancel"', squiggly, from=3-1, to=4-2]
        \arrow["\cancel", squiggly, from=2-3, to=3-3]
        \arrow["\cancel", squiggly, from=3-3, to=4-2]
      \end{tikzcd}
    }
    \caption{A converging critical pair in $\cox*$}
    \label{fig:critical-pairs-converging}
  \end{subfigure}
  \begin{subfigure}[b]{0.55\textwidth}
    \adjustbox{scale=\scalef,center}{
      % https://q.uiver.app/?q=WzAsMyxbMSwwLCJcXHRhdV8zXFx0YXVfMlxcdGF1XzNcXHRhdV8xIl0sWzAsMiwiXFx0YXVfMlxcdGF1XzNcXHRhdV8yXFx0YXVfMSJdLFszLDEsIlxcdGF1XzNcXHRhdV8yXFx0YXVfMVxcdGF1XzMiXSxbMCwxLCJicmFpZCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzAsMiwiYnJhaWQiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFsyLDEsIlxcbG9uZ2JyYWlkIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XV0=
      \begin{tikzcd}
        & {\tau_3\tau_2\tau_3\tau_1} \\
        &&& {\tau_3\tau_2\tau_1\tau_3} \\
        {\tau_2\tau_3\tau_2\tau_1}
        \arrow["braid"', squiggly, from=1-2, to=3-1]
        \arrow["braid", squiggly, from=1-2, to=2-4]
        \arrow["\longbraid", squiggly, from=2-4, to=3-1]
      \end{tikzcd}
    }
    \caption{A non-converging critical pair in $\cox*$ converges with $\longbraid$}
    \label{fig:critical-pairs-non-converging}
  \end{subfigure}

  \caption{Critical Pairs}
  \label{fig:critical-pairs}
\end{figure}

@@

% The Coxeter relations are a standard notion in the theory of group presentation~\todo{citation} -- even though we change
% the relations a bit, we will not lose the connection. In fact, we will prove that the new relations are equivalent, in a
% technical sense, to the standard Coxeter relations $\cox*$.
% The system has generators corresponding to $\swap$, $\cancel$
% and $\braid$, the problem of the non-converging critical pairs discussed previously is fixed by changing $\braid$ to be
% a slightly more general relation $\longbraid$.

\review{Further, we also inline the congruence closure in $\longcox$, allowing arbitrary reductions inside the list.}

\todo{but computation is usually done by using Coxeter matrices~\cite{davisGeometryTopologyCoxeter2008}.}

First, we need to define a helper function $n \downf k$.

@@

The result of this function is the sequence \([k + n - 1, k + n - 2, k + n - 3, \ldots, n]\). Since we think of the
number $m$ as the transposition swapping elements $(\el{m}, \el{m+1})$, the role of this helper function is to produce a
sequence of transpositions -- a permutation -- which moves element $\el{k + n}$ by $k$ places left, shifting all the
elements in between one place right (see~\Cref{fig:downf}). Then, the directed relation $\longcox$ is defined with the
following generators.

@@

Constructors $\longcancel$ and $\longswap$ correspond directly to the appropriate constructors of $\cox$ and can be
visualised in the same way as before. The remaining constructor uses the helper function to exchange the order of a long
sequence of transpositions and a single transposition afterwards. For example, for $n = 0$ and $k = 3$, it allows for
the reduction $[4, 3, 2, 1, 0, 4] \longcox [3, 4, 3, 2, 1, 0]$ (see~\Cref{fig:longcox} -- note the distinction between
wires, where numbers represent the values, and transpositions, where numbers represent which wires are crossing).

@@

      \def\nstrandsbr{6}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = \nstrandsbr,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick,
        name prefix=braid] at (4, 0)
      {braid={s_1, s_2, s_3, s_4, s_5, s_4}};
      % \draw[thick] % draws the top/bottom bars
      % ([xshift=-1ex]my braid.north west) --  ([xshift=1ex]my braid.north east)
      % ([xshift=-1ex]my braid.south west) --  ([xshift=1ex]my braid.south east);
      \foreach \n in {1,...,\nstrandsbl}{
          \pgfmathtruncatemacro{\nminusone}{\n - 1}
          \node at (braid-\n-s)[yshift = 2.8cm] {\nminusone};
        }
      % labels the bottom bar
      \node at (braid-1-e)[yshift = -2.8cm] {3};
      \node at (braid-2-e)[yshift = -2.8cm] {5};
      \node at (braid-3-e)[yshift = -2.8cm] {0};
      \node at (braid-4-e)[yshift = -2.8cm] {1};
      \node at (braid-5-e)[yshift = -2.8cm] {4};
      \node at (braid-6-e)[yshift = -2.8cm] {2};
    \end{tikzpicture}
    \caption{ $\longbraid$ with $n = 0$ and $k = 3$}
    \label{fig:longcox}
  \end{subfigure}
  \caption{Braiding diarams for modified Coxeter relations.}
  \label{fig:coxeter-braid-mod}
\end{figure}

@@

\begin{toappendix}
  \begin{definition}[$\longcoxstar$]
    \label{def:longcox-star}
    \begin{align*}
      \reflr{\longcox}
       & : \forall w \to w \longcoxstar w                                                                               \\
      \transr{\longcox}
       & : \forall w_{1}, w_{2}, w_{3} \to  w_{1} \longcox w_{2} \to w_{2} \longcoxstar w_{3} \to w_{1} \longcoxstar w_{3}
    \end{align*}
  \end{definition}
  \begin{definition}[$\longcoxplus$]
    \label{def:longcox-plus}
    \begin{align*}
      \relr{\longcoxplus}
       & : \forall w_{1}, w_{2} \to w_{1} \longcox w_{2} \to w_{1} \longcoxplus w_{2}
      \transr{\longcoxplus}
       & : \forall w_{1}, w_{2}, w_{3} \to  w_{1} \longcox w_{2} \to w_{2} \longcoxplus w_{3} \to w_{1} \longcoxplus w_{3}
    \end{align*}
  \end{definition}
\end{toappendix}

We define $\longcoxplus$ to be the transitive closure (\Cref{def:longcox-star}) and $\longcoxstar$ to be
reflexive-transitive closure (\Cref{def:longcox-plus})) of $\longcox$.

>>>>

% High-level explanation of technical devices
First, we will define the required notions of free groups and group presentations, and state some of their most
important properties. Then, we introduce our chosen \emph{Coxeter presentation} for $\Sn$. To solve the word problem for
$\Sn$, we will use a rewriting system, with a suitable, well behaved collection of reduction rules corresponding to the
Coxeter presentation. Finally, we describe the normal forms in this rewriting system, using Lehmer codes, and prove the
correspondence between them and the type $\Aut[\Fin[n]]$ of automorphisms on a finite set. The generators and relations
we use here will be used to quote back to 1 and 2-combinators in $\PiLang$ (see~\cref{sec:equivalence}).

@@

\begin{toappendix}
  \subsection{Groups}
  \label{subsec:groups}

  From universal algebra, a group is simply a set with a 0-ary constant $e$ (the neutral element), a binary operation
  $\blank\mult\blank$ for group multiplication, and a unary inverse operation $\inv{\blank}$. The neutral element has to
  satisfy unit and inverse laws, and the multiplication has to be associative (see~\cref{def:group}).

@@

\begin{toappendix}
  \begin{definition}
    \label{def:free-group}
    Given a set $A$, the free group $F(A)$ on it is given by a higher inductive type with the following point and path
    constructors. Notice the similarity with the definition of a group structure (\cref{def:group}), but note that each
    operation here is a generator for $F(A)$.
    \begin{itemize}
      \item An inclusion function $\eta_{A} : A \to F(A)$
      \item A multiplication function $m : F(A) \times F(A) \to F(A)$
      \item An element $e : F(A)$
      \item An inverse function $i : F(A) \to F(A)$
    \end{itemize}
    \smallskip
    \begin{itemize}
      \item For every $x, y, z : F(A)$, a path $\term{assoc} : m(x, m(y, z)) \id m(m(x, y), z)$
      \item For every $x : F(A)$, paths $\term{unitr} : m(x, e) \id x$ and $\term{unitl} : m(e, x) \id x$
      \item For every $x : F(A)$, paths $\term{invr} : m(x, i(x)) \id e$ and $\term{invl} : m(i(x), x) \id e$
      \item A 0-truncation, for every $x, y : F(A)$ and $p, q : x \id y$, a 2-path $\term{trunc} : p \id q$
    \end{itemize}
  \end{definition}
\end{toappendix}

@@

\begin{propositionrep}[Universal Property of $F(A)$]
  \label{prop:free-groups}
  Given a group $G$ and a map $f : A \to G$, there is a unique group
  homomorphism $\extend{f} : F(A) \to^G G$ such that $\extend{f} \comp \eta_A
    \htpy f$. Equivalently, composition with $\eta_A$ gives an equivalence $F(A)
    \to^G G \eqv A \to G$. Alternatively, the type of group homomorphisms $h :
    F(A) \to^G G$ satisfying $h \comp \eta_A \htpy f$ is contractible.
\end{propositionrep}

\begin{toappendix}
  % https://q.uiver.app/?q=WzAsMyxbMCwyLCJBIl0sWzAsMCwiRihBKSJdLFsyLDAsIkciXSxbMCwxLCJcXGV0YV9BIl0sWzAsMiwiZiIsMl0sWzEsMiwiXFxleHRlbmR7Zn0iLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJkYXNoZWQifX19XSxbMyw0LCJcXGlkIiwwLHsic2hvcnRlbiI6eyJzb3VyY2UiOjIwLCJ0YXJnZXQiOjIwfSwic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoibm9uZSJ9LCJoZWFkIjp7Im5hbWUiOiJub25lIn19fV1d
  \[\begin{tikzcd}
      {F(A)} && G \\
      \\
      A
      \arrow[""{name=0, anchor=center, inner sep=0}, "{\eta_A}", from=3-1, to=1-1]
      \arrow[""{name=1, anchor=center, inner sep=0}, "f"', from=3-1, to=1-3]
      \arrow["{\extend{f}}", dashed, from=1-1, to=1-3]
      \arrow["\id", Rightarrow, draw=none, from=0, to=1]
    \end{tikzcd}\]
\end{toappendix}

Following the universal-algebraic definition, in HoTT, we could use a naive higher inductive type to define the free
group, which enforces the group axioms by adding path constructors (see~\cref{def:free-group}). Using the induction
principle, we can easily verify the universal property. However, since this definition of $F(A)$ has lots of path
constructors corresponding to each group axiom, characterising its path space is difficult.

@@

Before, the only way to decide the equality of two elements in a group was to evaluate and check them on the nose, but
in a group presentation, this is reduced to a \emph{word problem}, that is, deciding whether one word -- a
representative of the equivalence class of the group's elements, can be reduced to another word, using the group's
relations. However, these equations are not directed, so it is not always possible to construct a well-behaved rewriting
system. In general, the word problem for groups is known to be undecidable.

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, s_1}};
      \node[font=\large] at (1, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1.6, 0)
      {braid={ 1, 1}};
    \end{tikzpicture}
    \caption{$\cancel$}
    \label{fig:coxeter-a}
  \end{subfigure}
  \begin{subfigure}[b]{0.4\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (0, 0)
      {braid={ s_1, 1}};
      \node[] at (0.7, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (1, 0)
      {braid={ 1, s_1 }};
      \node[font=\large] at (1.9, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (2.4, 0)
      {braid={ 1, s_1}};
      \node[] at (3.1, 0.7) {\(\dots\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 2,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.3cm,
        thick] at (3.4, 0)
      {braid={ s_1, 1}};
    \end{tikzpicture}
    \caption{$\swap$}
    \label{fig:coxeter-b}
  \end{subfigure}
  \begin{subfigure}[b]{0.25\textwidth}
    \centering
    \begin{tikzpicture}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (0, 0)
      {braid={ s_2, s_1, s_2}};
      \node[font=\large] at (1.4, 0.7) {\(\rightarrow\)};
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = 3,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick] at (2, 0)
      {braid={ s_1, s_2, s_1}};
    \end{tikzpicture}
    \caption{$\braid$}
    \label{fig:coxeter-c}
  \end{subfigure}
  \caption{Braiding diarams for Coxeter relations.}
  \label{fig:coxeter-braid}
\end{figure}

This construction is called a Coxeter presentation of $\Sn$. Writing it formally, we encode the rules discussed above
using a relation $\cox$ on $\List[\Fin[n]]$ (\cref{def:cox}), and then take its congruence closure $\cox*$
(\cref{def:coxstar}).

@@

For this to work, we first need the system to have the termination property, meaning that there are no infinite
reductions. We observe that after throwing out reflexivity and symmetry, the right hand sides of the relations $\cox*$
are strictly smaller than the left hand sides, in terms of the lexicographical ordering on words in $\Fin[n]$ (which is
well-founded). Thus, by directing the relation from left to right, we would get the termination property out of the box.
Second, we need the normal forms to be unique, so that we can get a normalisation function. This will be true if the
rewriting system is confluent -- meaning that all critical pairs, that is, terms with overlapping possible reduction
rules, have to converge. For example, in our system, the pair in~\Cref{fig:critical-pairs-converging} converges.
Unfortunately, this is not true for all critical pairs -- an  example is in~\Cref{fig:critical-pairs-non-converging},
where left and right endpoints are normal with respect to the $\cox*$ relation.

@@

% a + \UOLoverbrace{b +}[c + d]ˆx \UOLunderbrace{+ e}_y + f

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.35\textwidth}
    % https://q.uiver.app/?q=WzAsNixbMSwwLCJcXHRhdV8yXFx0YXVfMVxcdGF1XzJcXHRhdV8xXFx0YXVfMiJdLFswLDEsIlxcdGF1XzFcXHRhdV8yXFx0YXVfMVxcdGF1XzFcXHRhdV8yIl0sWzIsMSwiXFx0YXVfMlxcdGF1XzFcXHRhdV8xXFx0YXVfMlxcdGF1XzEiXSxbMCwyLCJcXHRhdV8xXFx0YXVfMlxcdGF1XzIiXSxbMSwzLCJcXHRhdV8xIl0sWzIsMiwiXFx0YXVfMlxcdGF1XzJcXHRhdV8xIl0sWzAsMSwiYnJhaWQiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFswLDIsImJyYWlkIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbMSwzLCJjYW5jZWwiLDIseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFszLDQsImNhbmNlbCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzIsNSwiY2FuY2VsIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XSxbNSw0LCJjYW5jZWwiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dXQ==
    \adjustbox{scale=\scalef,center}{
      \begin{tikzcd}
        & {\UOLoverline{\tau_2\tau_1}[\tau_2]\UOLunderline{\tau_1\tau_2}} \\
        {\tau_1\tau_2\overline{\tau_1\tau_1}\tau_2} && {\tau_2\underline{\tau_1\tau_1}\tau_2\tau_1} \\
        {\tau_1\overline{\tau_2\tau_2}} && {\underline{\tau_2\tau_2}\tau_1} \\
        & {\tau_1}
        \arrow["\braid"', squiggly, from=1-2, to=2-1]
        \arrow["\braid", squiggly, from=1-2, to=2-3]
        \arrow["\cancel"', squiggly, from=2-1, to=3-1]
        \arrow["\cancel"', squiggly, from=3-1, to=4-2]
        \arrow["\cancel", squiggly, from=2-3, to=3-3]
        \arrow["\cancel", squiggly, from=3-3, to=4-2]
      \end{tikzcd}
    }
    \caption{Converging critical pair}
    \label{fig:critical-pairs-converging}
  \end{subfigure}
  \begin{subfigure}[b]{0.55\textwidth}
    \adjustbox{scale=\scalef,center}{
      % https://q.uiver.app/?q=WzAsMyxbMSwwLCJcXHRhdV8zXFx0YXVfMlxcdGF1XzNcXHRhdV8xIl0sWzAsMiwiXFx0YXVfMlxcdGF1XzNcXHRhdV8yXFx0YXVfMSJdLFszLDEsIlxcdGF1XzNcXHRhdV8yXFx0YXVfMVxcdGF1XzMiXSxbMCwxLCJicmFpZCIsMix7InN0eWxlIjp7ImJvZHkiOnsibmFtZSI6InNxdWlnZ2x5In19fV0sWzAsMiwiYnJhaWQiLDAseyJzdHlsZSI6eyJib2R5Ijp7Im5hbWUiOiJzcXVpZ2dseSJ9fX1dLFsyLDEsIlxcbG9uZ2JyYWlkIiwwLHsic3R5bGUiOnsiYm9keSI6eyJuYW1lIjoic3F1aWdnbHkifX19XV0=
      \begin{tikzcd}
        & {\UOLoverline{\tau_3\tau_2}[\tau_3]\UOLunderline{\tau_1}} \\
        &&& {\underline{\tau_3\tau_2\tau_1\tau_3}} \\
        {\tau_2\tau_3\tau_2\tau_1}
        \arrow["\braid"', squiggly, from=1-2, to=3-1]
        \arrow["\swap", squiggly, from=1-2, to=2-4]
        \arrow["\longbraid", squiggly, from=2-4, to=3-1]
      \end{tikzcd}
    }
    \caption{Non-converging critical pair that converges with $\longbraid$}
    \label{fig:critical-pairs-non-converging}
  \end{subfigure}

  \caption{Critical Pairs in $\cox*$}
  \label{fig:critical-pairs}
\end{figure}

@@

First, we need to define a function $n \downf k$.

@@

The result of this function is the sequence \([k + n - 1, k + n - 2, k + n - 3, \ldots, n]\). Since we think of the
number $m$ as the transposition swapping elements $(\el{m}, \el{m+1})$, the role of this function is to produce a
sequence of transpositions which moves element $\el{k + n}$ left by $k$ places, shifting all the elements in between one
place right (see~\cref{fig:downf}). Then, the directed relation $\longcox$ is defined with the following generators,
inlining the congruence closure in $\longcox$, allowing arbitrary reductions inside the list.

@@

Constructors $\longcancel$ and $\longswap$ correspond directly to the appropriate constructors of $\cox$ and can be
visualised in the same way as before. The remaining constructor $\longbraid$ uses the $\downf$ function to exchange the
order of a long sequence of transpositions and a single transposition afterwards. For example, for $n = 0$ and $k = 3$,
it allows for the reduction $[4, 3, 2, 1, 0, 4] \longcox [3, 4, 3, 2, 1, 0]$ (see~\cref{fig:longcox} -- note the
distinction between wires, where numbers represent the values, and transpositions, where numbers represent which wires
are crossing).

@@

      \def\nstrandsbr{6}
      \pic[local bounding box=my braid,braid/.cd,
        number of strands = \nstrandsbr,
        width = 0.4cm,
        height = 0.4cm,
        border height = 0.1cm,
        thick,
        name prefix=braid] at (4, 0)
      {braid={s_1, s_2, s_3, s_4, s_5, s_4}};
      % \draw[thick] % draws the top/bottom bars
      % ([xshift=-1ex]my braid.north west) --  ([xshift=1ex]my braid.north east)
      % ([xshift=-1ex]my braid.south west) --  ([xshift=1ex]my braid.south east);
      \foreach \n in {1,...,\nstrandsbl}{
          \pgfmathtruncatemacro{\nminusone}{\n - 1}
          \node at (braid-\n-s)[yshift = 2.8cm] {\nminusone};
        }
      % labels the bottom bar
      \node at (braid-1-e)[yshift = -2.8cm] {3};
      \node at (braid-2-e)[yshift = -2.8cm] {5};
      \node at (braid-3-e)[yshift = -2.8cm] {0};
      \node at (braid-4-e)[yshift = -2.8cm] {1};
      \node at (braid-5-e)[yshift = -2.8cm] {4};
      \node at (braid-6-e)[yshift = -2.8cm] {2};
    \end{tikzpicture}
    \caption{ $\longbraid$ with $n = 0$ and $k = 3$}
    \label{fig:longcox}
  \end{subfigure}
  \caption{Braiding diagrams for modified Coxeter relations.}
  \label{fig:coxeter-braid-mod}
\end{figure}

@@

\begin{toappendix}
  \begin{definition}[$\longcoxstar$]
    \label{def:longcox-star}
    \begin{align*}
      \reflr{\longcox}
       & : \forall w \to w \longcoxstar w                                                                                  \\
      \transr{\longcox}
       & : \forall w_{1}, w_{2}, w_{3} \to  w_{1} \longcox w_{2} \to w_{2} \longcoxstar w_{3} \to w_{1} \longcoxstar w_{3}
    \end{align*}
  \end{definition}

  \begin{definition}[$\longcoxplus$]
    \label{def:longcox-plus}
    \begin{align*}
      \relr{\longcoxplus}
       & : \forall w_{1}, w_{2} \to w_{1} \longcox w_{2} \to w_{1} \longcoxplus w_{2}                                      \\
      \transr{\longcoxplus}
       & : \forall w_{1}, w_{2}, w_{3} \to  w_{1} \longcox w_{2} \to w_{2} \longcoxplus w_{3} \to w_{1} \longcoxplus w_{3}
    \end{align*}
  \end{definition}
\end{toappendix}

For the relation $\longcox$, we define its transitive closure to be $\longcoxplus$ (\cref{def:longcox-plus}) and its
reflexive-transitive closure to be $\longcoxstar$ (\cref{def:longcox-star}).

Despite the increased complexity of the generators, the rewriting system $(\List[\Fin[n]],\longcox)$ has the properties
we desire. It satisfies local confluence, that is, the Church-Rosser (diamond) property, and it is terminating, so, by
Newman's lemma, it produces a unique normal form. We follow the terminology
of~\cite*{huetConfluentReductionsAbstract1980a,krausCoherenceWellFoundednessTaming2020} to state our results formally.
